Even-point Multi-loop Unitarity and its Applications: Exponentiation, Anomalies and Evanescence

### 2023-07-07 eventPointTwoLoop.tex
typos and bird change
peacock -> ostrich

\begin{figure}[t]
    \centering
    \begin{equation*}\Omega_{(2,4)} = \left\{\scaleIntBscalar{}{}{}{},\scaleIntCscalar{}{}{}{} \right\}\end{equation*}
    \caption{Recursive one-loop integrals contributing to the  two-loop four-point calculation in even-point effective field theories, we refer to as the peacock integral and double-bubble from left to right.}
    \label{fig:contrib2Loop}
\end{figure}

@@

    \caption{Graphical depiction of the the peacock integral. Every exposed internal edge represents a propagator in the integrand.}
    \label{fig:peacock}

@@

A similar procedure can be applied to the peacock type diagrams of \Fig{fig:peacock}. However, the integration procedure is a little more delicate than the $I^{\text{ex}.}_{\text{2bub}}$ of \eqn{intg2bub}.  As $I^{\text{ex}.}_{\text{2bub}}$ could be expressed as an iterated bubble, we only needed to consider {integer powers} of the denominators when constructing the recursion relations. In contrast, peacock integrals  will lead to {non-integer}, $\epsilon$-dependent powers of loop propagators. We are therefore interested in performing a tensor reduction on the triangle integral,

@@

As we argued in the introduction, two-loop amplitudes for even-point theories, like NLSM, are completely determined by two recursive integrals, the {double-bubble} and the {peacock-diagram}, modulo theory-dependent kinematic numerators. For NLSM, the relevant integrals are as follows:

\begin{align}
\scaleIntCsmall &= \sum_{\text{states}}\int \frac{d^D l_{1}d^D l_{2}}{(2\pi)^{2D}}\frac{\mathcal{A}^{\text{NLSM}}_{(p_4|12|p_3)}\mathcal{A}^{\text{NLSM}}_{(\bar{p}_1|\bar{p}_4\bar{p}_3|\bar{p}_2)}\mathcal{A}^{\text{NLSM}}_{(p_2|34|p_1)}}{l_1^2(l_1+k_{12})^2l_2^2(l_2+k_{12})^2}
\\
\scaleIntBscalarsmall{1}{2}{3}{4}&=\sum_{\text{states}}\int \frac{d^D l_{1}d^D l_{2}}{(2\pi)^{2D}}\frac{\mathcal{A}^{\text{NLSM}}_{(2|q_4\bar{q}_3|\bar{q}_1)}\mathcal{A}^{\text{NLSM}}_{(1|\bar{q}_4q_3|\bar{q}_2)}\mathcal{A}^{\text{NLSM}}_{(q_2|34|q_1)}}{l_1^2(l_1+l_2+k_1)^2l_2^2(l_2+k_{12})^2}
\end{align}
where the internal momenta appearing in the NLSM operators, $\bar{p}_i= -p_i$ and $\bar{q}_i = -q_i$,  are defined in terms of the two loop momenta as follows:
\begin{align}
p_1 & = l_2+k_{12} \qquad p_2 =-l_2\qquad p_3 =l_1\qquad p_4 = -(l_1+k_{12})\,,
\\
q_1&= l_2+k_{12}
 \qquad q_2 = -l_2 
\qquad q_3 = l_1
\qquad q_4 =  - (l_1+l_2+k_1)\,.
\end{align}
Due to the simplicity of scalar theories like NLSM, the state sum for the double-bubble numerator is quite simple, and can be expressed concisely below:
\begin{equation}\label{eq:NLSM2Bub}
\begin{aligned}
\text{Cut}\left(\! \scaleIntCsmall \! \right)&= \sum_{\text{states}}\mathcal{A}^{\text{NLSM}}_{(p_4|12|p_3)}\mathcal{A}^{\text{NLSM}}_{(\bar{p}_1|\bar{p}_4\bar{p}_3|\bar{p}_2)}\mathcal{A}^{\text{NLSM}}_{(p_2|34|p_1)}
\\
&=C^{\text{2box}}_{(12|34)} \left[\tau^{(1)}_3 \tau_{13}\tau^{(3)}_{1}+\tau^{(1)}_3 \tau_{23}\tau^{(3)}_{2}+\tau^{(2)}_3 \tau_{23}\tau^{(3)}_{1}+\tau^{(2)}_3 \tau_{13}\tau^{(3)}_{2}\right]
\\
&+C^{\text{2box}}_{(12|43)}\left[\tau^{(2)}_3 \tau_{23}\tau^{(3)}_{2}+\tau^{(2)}_3 \tau_{13}\tau^{(3)}_{1}+\tau^{(1)}_3 \tau_{23}\tau^{(3)}_{1}+\tau^{(1)}_3 \tau_{13}\tau^{(3)}_{2}\right]
\end{aligned}
\end{equation}
where we have introduced the following notation above that combines internal and external momenta, $\tau^{(i)}_j = (k_i  + p_j)^2$ and $\tau_{ij} = (p_i + p_j)^2$. Plugging in the color-dressed NLSM amplitudes, the same can be done for the peacock-diagram cut, giving us

@@

\paragraph{\textbf{Reduction}} Just as with one-loop, we will now reduce the integrals of \eqn{eq:NLSM2loop} to the a basis of $D$-dimensional scalar integrals using the EMU loop reduction. The double-bubble contribution yields the following:
\begin{equation}
\label{eq:NLSM2bub}
\begin{aligned}
\scaleIntCsmall &= f_{\pi}^{-6}C^{\text{2box}}_{(12|34)} \left[\frac{(s_{12}I_2^D(k_{12}))^2}{2}\left(\frac{s_{14}-s_{13}}{(D-1)^2}+s_{12}\right)\right]
\\
&+f_{\pi}^{-6}C^{\text{2box}}_{(12|43)} \left[\frac{(s_{12}I_2^D(k_{12}))^2}{2}\left(\frac{s_{13}-s_{14}}{(D-1)^2}+s_{12}\right)\right]
\end{aligned}
\end{equation}
Likewise, we can perform a similar reduction to the dunce cap integrals -- but with a small twist. The double-bubble integral above is completely separable, which allows one to treat the tensor reduction of each loop integral as independent. This is not so for the peacock-diagram integral. The peacock-diagram carries an internal bubble, $I^D_2(q)$, with a loop dependent scale factor of $q=l_2+k_1$. Thus, we must first reduce the powers of $l_1$ and {then} perform a tensor reduction on all the remaining $l_2$ factors. Doing so yields the following result:

@@

where we have defined the scalar peacock-diagram integral, $[I_3\circ I_2]^D(k_{12})$, as a $D$-dimensional convolution of $I_2^D$ and $I_3^D$, provided below:

@@

\subsubsection{One-loop DBIVA}\label{sec:1loopDBIU}
Analogous to our procedure in the previous section where we defined $\mathcal{A}^{\text{NLSM}}_{(1|23|4)}$, first we will define a set of four-point operators for each distinct set of particle interaction. The $D$-dimensional contacts needed for DBIVA amplitudes at one-loop are as follows:
\begin{align}
\mathcal{M}(1_\gamma,2_\gamma,3_\gamma,4_\gamma) &= 2\text{tr}(F_1F_2F_3F_4) - \frac{1}{2}\text{tr}(F_1F_2)\text{tr}(F_3F_4)+\text{cyc}(1,2,3) \equiv t_8 F^4
\\
\mathcal{M}(1_\lambda,2_\gamma,3_\gamma,4_{\overline{\lambda}}) &= s_{13}\bar{u}_1(\slashed{\varepsilon}_2\slashed{k}_{12}\slashed{\varepsilon}_3) \bar{v}_4 + s_{12}\bar{u}_1(\slashed{\varepsilon}_3\slashed{k}_{13}\slashed{\varepsilon}_2) \bar{v}_4
\\
\mathcal{M}(1_X,2_\gamma,3_\gamma,4_{\overline{X}}) &= 2 (k_1 F_2 F_3 k_1) +2 (k_4 F_3 F_2 k_4)
\end{align}
where we have introduced notation $(k_a F_b F_c k_a) \equiv k_a^\mu F^{\mu\nu}_bF^{\nu\rho}_c k_a^\rho$ for the mixed scalar-vector amplitude. The particle content is labeled by $\gamma$ for the BI photons, $\lambda$ for the VA fermions, and $X$ for the Dirac scalars. With these tree-level amplitudes in hand, we define the following set of operators needed for integrand construction:
\begin{align}
\mathcal{M}^{\gamma \gamma \gamma \gamma }_{(1|23|4)} &= \mathcal{M}(1_\gamma,2_\gamma,3_\gamma,4_\gamma)   
\\
\mathcal{M}^{\lambda \gamma \gamma \bar{\lambda} }_{(1|23|4)} &= \mathcal{M}(1_\lambda,2_\gamma,3_\gamma,4_{\overline{\lambda}})
\\
\mathcal{M}^{X \gamma \gamma \bar{X} }_{(1|23|4)} &= \mathcal{M}(1_X,2_\gamma,3_\gamma,4_{\overline{X}}) 
\end{align}
While these are a subset of the four-point operators we will use in the two-loop construction, they are sufficient for all the one-loop external-photon amplitudes. To construct the integrands, we will use the $D$-dimensional state sums for vectors and fermions, which we provide below:
\begin{align}
\sum_{\text{states}}\varepsilon^\mu_{(l)}\varepsilon^\nu_{(-l)} &= \eta^{\mu\nu} - \frac{l^\mu q^\nu+l^\nu q^\mu}{l\cdot q},
\\
\sum_{\text{states}}u_{(l)}\bar{v}_{(-l)} &= \frac{1}{2}(1\pm \Gamma_5)\Gamma_\mu l^\mu 
\end{align}
where $q^2=0$ is a null-reference momentum. Here, $\Gamma_\mu$ are $D$-dimensional gamma matrices endowed with all the normal Clifford algebraic relations. Since we want to keep this as $D$-dimensional as possible, we define $\Gamma_5$ as the symbol representing the $(D+1)^{th}$ gamma matrix that anti-commutes with all other $\Gamma_\mu$. Using this, we have added in a chiral projection state operator $P_{\pm}=\frac{1}{2}(1\pm \Gamma_5)$ that will be relevant when computing the two-loop fermion contribution. To see why, we note that since we are only computing external photon amplitudes, the loop contribution must be {parity even}. Concretely, this means that if there is a single chiral trace, the $\Gamma_5$ contribution must integrate to zero:
\begin{equation}
2\text{tr}_{\pm}[\cdots] \equiv \text{tr}[(1\pm \Gamma_5)\cdots]  \xrightarrow{\int d\Pi_{\text{loop}}} \frac{1}{2}\text{tr}[\cdots]
\end{equation}
The property will significantly simplify the two-loop reduction in the presence of {single} chiral trace. However, at two-loop we can also get multi-trace contributions. In this case, the parity odd contribution (sourced by odd powers of $\Gamma_5$) must vanish after integration as follows:
\begin{equation}
4\text{tr}_{\pm}[\cdots] \text{tr}_{\pm}[\cdots]  \xrightarrow{\int d\Pi_{\text{loop}}} \text{tr}[\cdots]\text{tr}[\cdots]+\text{tr}[\Gamma_5\cdots]\text{tr}[\Gamma_5\cdots]
\end{equation}
The second term is also parity even, and will contribute $D$-dimensional Gram determinants in the presence of two internal fermion loops. While in principle this term is relevant for two-loop diagrams with internal fermions, due to the simplicity of $\mathcal{N}=4$ DBIVA state sums, we won't need to account for it in our analysis at two-loop.

@@

and similarly so for the peacock-diagram integral contribution:

@@

Since there are no loop momenta interfering with the tensor structures of the external photons, the result of integration will just be proportional to a $(t_8F^4)$ tensor, which is manifestly $U(1)$ duality invariant. Thus, as promised, adding in $\mathcal{N}=4$ states cancels the $U(1)$ anomaly present in the pure Born-Infeld $S$-matrix. After applying the tensor reduction to the peacock-diagram, we obtain the following expression for the two diagrams:

@@

\subsubsection{Two-loop $\mathcal{N}=4$ DBIVA} \label{sec:DBIvDC2loop}
At two-loop it sufficient to show that replacing the color factors reproduces the integrals we found above with the unitarity construction. Starting with the NLSM integrands in \eqn{eq:NLSM2bub} and \eqn{eq:NLSMdunce}, we make the same replacement of color factors post integration as was done at one-loop.  We carry this out first for the double-bubble, and find that the full $D$-dimensional NLSM integral simplifies dramatically:
\begin{equation}
\begin{aligned}
\scaleIntCsmall \bigg|^{C_g \rightarrow N^{\mathcal{N}=4}_g}  \!\!&= N^{(12|34)}_{\mathcal{N}=4}\left[\frac{(s_{12}I_2^D(k_{12}))^2}{2}\left(\frac{s_{14}-s_{13}}{(D-1)^2}+s_{12}\right)\right]
\\
&+N^{(12|43)}_{\mathcal{N}=4}\left[\frac{(s_{12}I_2^D(k_{12}))^2}{2}\left(\frac{s_{13}-s_{14}}{(D-1)^2}+s_{12}\right)\right]
\\
&=s_{12}^4 (I_2^{D}(k_{12}))^2(t_8 F^4)^{\text{(max)}}_{(1234)}   \equiv \scaleIntCtune{}{hgreen}{}{hgreen} 
\end{aligned}
\end{equation}
The cancellation between dimension dependent factors is even more startling for the peacock-diagram integral:
\begin{equation}
\begin{aligned}
\scaleIntBscalarsmall{1}{2}{3}{4}\bigg|^{C_g \rightarrow N^{\mathcal{N}=4}_g} \!\!&= N^{(12|34)}_{\mathcal{N}=4}\frac{s_{12}}{6} \left[\frac{(D-1)(D-4)s_{14}+2(D-2)^2 s_{13}}{(D-1)(4-3D)}\right][I_3\circ I_2]^D(k_{12})
\\
&+N^{(12|34)}_{\mathcal{N}=4}\frac{s_{12}}{6} \left[\frac{(D-1)(D-4)s_{13}+2(D-2)^2 s_{14}}{(D-1)(4-3D)}\right][I_3\circ I_2]^D(k_{12})
\\
&+N^{([12]|34)}_{\mathcal{N}=4}\left[\frac{s_{12}^2}{6}\frac{D+1}{D-1}\right][I_3\circ I_2]^D(k_{12})
\\
&=\frac{s_{12}^3}{3}[I_3\circ I_2]^{D}(k_{12})(t_8 F^4)^{\text{(max)}}_{(1234)} \equiv \scaleIntBtune{}{}{}{}{hgreen}{hgreen}{hgreen}{hgreen} 
\end{aligned}
\end{equation}
This alone is sufficient to demonstrate the validity of the double-copy, as these integrated quantities are exactly the same as those produced via generalized unitarity of $\mathcal{N}=4$ DBIVA at two-loop in \eqn{eq:N42bub} and \eqn{eq:N4dunce}. We emphasize that based on our analysis, this consistency of the double-copy at two loop appears to hold in {any} dimension, as all the $D$-dependent prefactors drop out upon replacing the gauge theory color factors with $\mathcal{N}=4$ numerators. Considering the consistency of these two construction, this also serves as strong evidence for the existence of color-dual representation for two-loop pion integrands. We leave identifying such valid representation as an enticing future direction worth investigation.

>>>>

\begin{figure}[t]
    \centering
    \begin{equation*}\Omega_{(2,4)} = \left\{\scaleIntBscalar{}{}{}{},\scaleIntCscalar{}{}{}{} \right\}\end{equation*}
    \caption{Recursive one-loop integrals contributing to the  two-loop four-point calculation in even-point effective field theories, we refer to as the ostrich integral and double-bubble from left to right.}
    \label{fig:contrib2Loop}
\end{figure}

@@

    \caption{Graphical depiction of the the ostrich integral. Every exposed internal edge represents a propagator in the integrand.}
    \label{fig:ostrich}

@@

A similar procedure can be applied to the ostrich type diagrams of \Fig{fig:ostrich}. However, the integration procedure is a little more delicate than the $I^{\text{ex}.}_{\text{2bub}}$ of \eqn{intg2bub}.  As $I^{\text{ex}.}_{\text{2bub}}$ could be expressed as an iterated bubble, we only needed to consider {integer powers} of the denominators when constructing the recursion relations. In contrast, ostrich integrals  will lead to {non-integer}, $\epsilon$-dependent powers of loop propagators. We are therefore interested in performing a tensor reduction on the triangle integral,

@@

As we argued in the introduction, two-loop amplitudes for even-point theories, like NLSM, are completely determined by two recursive integrals, the {double-bubble} and the {ostrich-diagram}, modulo theory-dependent kinematic numerators. For NLSM, the relevant integrals are as follows:

\begin{align}
\scaleIntCsmall &= \sum_{\text{states}}\int \frac{d^D l_{1}d^D l_{2}}{(2\pi)^{2D}}\frac{\mathcal{A}^{\text{NLSM}}_{(p_4|12|p_3)}\mathcal{A}^{\text{NLSM}}_{(\bar{p}_1|\bar{p}_4\bar{p}_3|\bar{p}_2)}\mathcal{A}^{\text{NLSM}}_{(p_2|34|p_1)}}{l_1^2(l_1+k_{12})^2l_2^2(l_2+k_{12})^2}
\\
\scaleIntBscalarsmall{1}{2}{3}{4}&=\sum_{\text{states}}\int \frac{d^D l_{1}d^D l_{2}}{(2\pi)^{2D}}\frac{\mathcal{A}^{\text{NLSM}}_{(2|q_4\bar{q}_3|\bar{q}_1)}\mathcal{A}^{\text{NLSM}}_{(1|\bar{q}_4q_3|\bar{q}_2)}\mathcal{A}^{\text{NLSM}}_{(q_2|34|q_1)}}{l_1^2(l_1+l_2+k_1)^2l_2^2(l_2+k_{12})^2}
\end{align}
where the internal momenta appearing in the NLSM operators, $\bar{p}_i= -p_i$ and $\bar{q}_i = -q_i$,  are defined in terms of the two loop momenta as follows:
\begin{align}
p_1 & = l_2+k_{12} \qquad p_2 =-l_2\qquad p_3 =l_1\qquad p_4 = -(l_1+k_{12})\,,
\\
q_1&= l_2+k_{12}
 \qquad q_2 = -l_2 
\qquad q_3 = l_1
\qquad q_4 =  - (l_1+l_2+k_1)\,.
\end{align}
Due to the simplicity of scalar theories like NLSM, the state sum for the double-bubble numerator is quite simple, and can be expressed concisely below:
\begin{equation}\label{eq:NLSM2Bub}
\begin{aligned}
\text{Cut}\left(\! \scaleIntCsmall \! \right)&= \sum_{\text{states}}\mathcal{A}^{\text{NLSM}}_{(p_4|12|p_3)}\mathcal{A}^{\text{NLSM}}_{(\bar{p}_1|\bar{p}_4\bar{p}_3|\bar{p}_2)}\mathcal{A}^{\text{NLSM}}_{(p_2|34|p_1)}
\\
&=C^{\text{2box}}_{(12|34)} \left[\tau^{(1)}_3 \tau_{13}\tau^{(3)}_{1}+\tau^{(1)}_3 \tau_{23}\tau^{(3)}_{2}+\tau^{(2)}_3 \tau_{23}\tau^{(3)}_{1}+\tau^{(2)}_3 \tau_{13}\tau^{(3)}_{2}\right]
\\
&+C^{\text{2box}}_{(12|43)}\left[\tau^{(2)}_3 \tau_{23}\tau^{(3)}_{2}+\tau^{(2)}_3 \tau_{13}\tau^{(3)}_{1}+\tau^{(1)}_3 \tau_{23}\tau^{(3)}_{1}+\tau^{(1)}_3 \tau_{13}\tau^{(3)}_{2}\right]
\end{aligned}
\end{equation}
where we have introduced the following notation above that combines internal and external momenta, $\tau^{(i)}_j = (k_i  + p_j)^2$ and $\tau_{ij} = (p_i + p_j)^2$. Plugging in the color-dressed NLSM amplitudes, the same can be done for the ostrich-diagram cut, giving us

@@

\paragraph{\textbf{Reduction}} Just as with one-loop, we will now reduce the integrals of \eqn{eq:NLSM2loop} to the a basis of $D$-dimensional scalar integrals using the EMU loop reduction. The double-bubble contribution yields the following:
\begin{equation}
\label{eq:NLSM2bub}
\begin{aligned}
\scaleIntCsmall &= f_{\pi}^{-6}C^{\text{2box}}_{(12|34)} \left[\frac{(s_{12}I_2^D(k_{12}))^2}{2}\left(\frac{s_{14}-s_{13}}{(D-1)^2}+s_{12}\right)\right]
\\
&+f_{\pi}^{-6}C^{\text{2box}}_{(12|43)} \left[\frac{(s_{12}I_2^D(k_{12}))^2}{2}\left(\frac{s_{13}-s_{14}}{(D-1)^2}+s_{12}\right)\right]
\end{aligned}
\end{equation}
Likewise, we can perform a similar reduction to the dunce cap integrals -- but with a small twist. The double-bubble integral above is completely separable, which allows one to treat the tensor reduction of each loop integral as independent. This is not so for the ostrich-diagram integral. The ostrich-diagram carries an internal bubble, $I^D_2(q)$, with a loop dependent scale factor of $q=l_2+k_1$. Thus, we must first reduce the powers of $l_1$ and {then} perform a tensor reduction on all the remaining $l_2$ factors. Doing so yields the following result:

@@

where we have defined the scalar ostrich-diagram integral, $[I_3\circ I_2]^D(k_{12})$, as a $D$-dimensional convolution of $I_2^D$ and $I_3^D$, provided below:

@@

\subsubsection{One-loop DBIVA}\label{sec:1loopDBIU}
Analogous to our procedure in the previous section where we defined $\mathcal{A}^{\text{NLSM}}_{(1|23|4)}$, first we will define a set of four-point operators for each distinct set of particle interaction. The $D$-dimensional contacts needed for DBIVA amplitudes at one-loop are as follows:
\begin{align}
\mathcal{M}(1_\gamma,2_\gamma,3_\gamma,4_\gamma) &= 2\text{tr}(F_1F_2F_3F_4) - \frac{1}{2}\text{tr}(F_1F_2)\text{tr}(F_3F_4)+\text{cyc}(1,2,3) \equiv t_8 F^4
\\
\mathcal{M}(1_\lambda,2_\gamma,3_\gamma,4_{\overline{\lambda}}) &= s_{13}\bar{u}_1(\slashed{\varepsilon}_2\slashed{k}_{12}\slashed{\varepsilon}_3) \bar{v}_4 + s_{12}\bar{u}_1(\slashed{\varepsilon}_3\slashed{k}_{13}\slashed{\varepsilon}_2) \bar{v}_4
\\
\mathcal{M}(1_X,2_\gamma,3_\gamma,4_{\overline{X}}) &= 2 (k_1 F_2 F_3 k_1) +2 (k_4 F_3 F_2 k_4)
\end{align}
where we have introduced notation $(k_a F_b F_c k_a) \equiv k_a^\mu F^{\mu\nu}_bF^{\nu\rho}_c k_a^\rho$ for the mixed scalar-vector amplitude. The particle content is labeled by $\gamma$ for the BI photons, $\lambda$ for the VA fermions, and $X$ for the Dirac scalars. With these tree-level amplitudes in hand, we define the following set of operators needed for integrand construction:
\begin{align}
\mathcal{M}^{\gamma \gamma \gamma \gamma }_{(1|23|4)} &= \mathcal{M}(1_\gamma,2_\gamma,3_\gamma,4_\gamma)   
\\
\mathcal{M}^{\lambda \gamma \gamma \bar{\lambda} }_{(1|23|4)} &= \mathcal{M}(1_\lambda,2_\gamma,3_\gamma,4_{\overline{\lambda}})
\\
\mathcal{M}^{X \gamma \gamma \bar{X} }_{(1|23|4)} &= \mathcal{M}(1_X,2_\gamma,3_\gamma,4_{\overline{X}}) 
\end{align}
While these are a subset of the four-point operators we will use in the two-loop construction, they are sufficient for all the one-loop external-photon amplitudes. To construct the integrands, we will use the $D$-dimensional state sums for vectors and fermions, which we provide below:
\begin{align}
\sum_{\text{states}}\varepsilon^\mu_{(l)}\varepsilon^\nu_{(-l)} &= \eta^{\mu\nu} - \frac{l^\mu q^\nu+l^\nu q^\mu}{l\cdot q},
\\
\sum_{\text{states}}u_{(l)}\bar{v}_{(-l)} &= \frac{1}{2}(1\pm \Gamma_5)\Gamma_\mu l^\mu 
\end{align}
where $q^2=0$ is a null-reference momentum. Here, $\Gamma_\mu$ are $D$-dimensional gamma matrices endowed with all the normal Clifford algebraic relations. Since we want to keep this as $D$-dimensional as possible, we define $\Gamma_5$ as the symbol representing the $(D+1)^{th}$ gamma matrix that anti-commutes with all other $\Gamma_\mu$. Using this, we have added in a chiral projection state operator $P_{\pm}=\frac{1}{2}(1\pm \Gamma_5)$ that will be relevant when computing the two-loop fermion contribution. To see why, we note that since we are only computing external photon amplitudes, the loop contribution must be {parity even}. Concretely, this means that if there is a single chiral trace, the $\Gamma_5$ contribution must integrate to zero:
\begin{equation}
2\text{tr}_{\pm}[\cdots] \equiv \text{tr}[(1\pm \Gamma_5)\cdots]  \xrightarrow{\int d\Pi_{\text{loop}}} \text{tr}[\cdots]
\end{equation}
The property will significantly simplify the two-loop reduction in the presence of {single} chiral trace. However, at two-loop we can also get multi-trace contributions. In this case, the parity odd contribution (sourced by odd powers of $\Gamma_5$) must vanish after integration as follows:
\begin{equation}
4\text{tr}_{\pm}[\cdots] \text{tr}_{\pm}[\cdots]  \xrightarrow{\int d\Pi_{\text{loop}}} \text{tr}[\cdots]\text{tr}[\cdots]+\text{tr}[\Gamma_5\cdots]\text{tr}[\Gamma_5\cdots]
\end{equation}
The second term is also parity even, and will contribute $D$-dimensional Gram determinants in the presence of two internal fermion loops. While in principle this term is relevant for two-loop diagrams with internal fermions, due to the simplicity of $\mathcal{N}=4$ DBIVA state sums, we won't need to account for it in our analysis at two-loop.

@@

and similarly so for the ostrich-diagram integral contribution:

@@

Since there are no loop momenta interfering with the tensor structures of the external photons, the result of integration will just be proportional to a $(t_8F^4)$ tensor, which is manifestly $U(1)$ duality invariant. Thus, as promised, adding in $\mathcal{N}=4$ states cancels the $U(1)$ anomaly present in the pure Born-Infeld $S$-matrix. After applying the tensor reduction to the ostrich-diagram, we obtain the following expression for the two diagrams:

@@

\subsubsection{Two-loop $\mathcal{N}=4$ DBIVA} \label{sec:DBIvDC2loop}
At two-loop it sufficient to show that replacing the color factors reproduces the integrals we found above with the unitarity construction. Starting with the NLSM integrands in \eqn{eq:NLSM2bub} and \eqn{eq:NLSMdunce}, we make the same replacement of color factors post integration as was done at one-loop.  We carry this out first for the double-bubble, and find that the full $D$-dimensional NLSM integral simplifies dramatically:
\begin{equation}
\begin{aligned}
\scaleIntCsmall \bigg|^{C_g \rightarrow N^{\mathcal{N}=4}_g}  \!\!&= N^{(12|34)}_{\mathcal{N}=4}\left[\frac{(s_{12}I_2^D(k_{12}))^2}{2}\left(\frac{s_{14}-s_{13}}{(D-1)^2}+s_{12}\right)\right]
\\
&+N^{(12|43)}_{\mathcal{N}=4}\left[\frac{(s_{12}I_2^D(k_{12}))^2}{2}\left(\frac{s_{13}-s_{14}}{(D-1)^2}+s_{12}\right)\right]
\\
&=s_{12}^4 (I_2^{D}(k_{12}))^2(t_8 F^4)^{\text{(max)}}_{(1234)}   \equiv \scaleIntCtune{}{hgreen}{}{hgreen} 
\end{aligned}
\end{equation}
The cancellation between dimension dependent factors is even more startling for the ostrich-diagram integral:
\begin{equation}
\begin{aligned}
\scaleIntBscalarsmall{1}{2}{3}{4}\bigg|^{C_g \rightarrow N^{\mathcal{N}=4}_g} \!\!&= N^{(12|34)}_{\mathcal{N}=4}\frac{s_{12}}{6} \left[\frac{(D-1)(D-4)s_{14}+2(D-2)^2 s_{13}}{(D-1)(4-3D)}\right][I_3\circ I_2]^D(k_{12})
\\
&+N^{(12|34)}_{\mathcal{N}=4}\frac{s_{12}}{6} \left[\frac{(D-1)(D-4)s_{13}+2(D-2)^2 s_{14}}{(D-1)(4-3D)}\right][I_3\circ I_2]^D(k_{12})
\\
&+N^{([12]|34)}_{\mathcal{N}=4}\left[\frac{s_{12}^2}{6}\frac{D+1}{D-1}\right][I_3\circ I_2]^D(k_{12})
\\
&=\frac{s_{12}^3}{3}[I_3\circ I_2]^{D}(k_{12})(t_8 F^4)^{\text{(max)}}_{(1234)} \equiv \scaleIntBtune{}{}{}{}{hgreen}{hgreen}{hgreen}{hgreen} 
\end{aligned}
\end{equation}
This alone is sufficient to demonstrate the validity of the double-copy, as these integrated quantities are exactly the same as those produced via generalized unitarity of $\mathcal{N}=4$ DBIVA at two-loop in \eqn{eq:N42bub} and \eqn{eq:N4dunce}. We emphasize that based on our analysis, this consistency of the double-copy at two loop appears to hold in {any} dimension, as all the $D$-dependent prefactors drop out upon replacing the gauge theory color factors with $\mathcal{N}=4$ numerators. Considering the consistency of these two construction, this also serves as strong evidence for the existence of color-dual representation for two-loop pion integrands. We leave identifying such valid representation as an enticing future direction worth investigation.
